Impacts of Month, Grocery Vendor, Presale Prices, and Historical Pricing on Discounted Egg Dozen Prices

### 2024-12-13 paper/paper.qmd
amended month graphs to be in order

@fig-vendorprices shows a boxplot of the sale pricing of a dozen eggs across the 8 vendors. From this graph, we can observe that T&T has the lowest prices overall and Save On Foods the highest. There are also differences in the range of prices offered, with T&T and Metro having much wider price ranges compared to Galleria and Save On Foods, which have highly consistent sale pricing.

@@

analysis_data |> 
  ggplot(aes(x = month)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Month",
       y = "Number of Sales")
```

@@

coeff <- c(0, 0.36, 0.83, 1.03, 1.72, 0.31, 1.13, 0.58)
months <- c("April", "May", "June", "July", "August", "September", "October", "November")
month_results <- data.frame(Months = months, Coefficients = coeff)

>>>>

@fig-vendorprices shows the summarized sale pricing of a dozen eggs across the 8 vendors. From this graph, we can observe that T&T has the lowest prices overall and Save On Foods the highest. There are also differences in the range of prices offered, with T&T and Metro having much wider price ranges compared to Galleria and Save On Foods, which have highly consistent sale pricing.

@@

month_sales <- analysis_data |> count(month)
month_sales <- month_sales %>%
  mutate(month = recode(month,
                        Mar = 3,
                        Apr = 4,
                        May = 5,
                        Jun = 6,
                        Jul = 7,
                        Aug = 8, 
                        Sep = 9,
                        Oct = 10,
                        Nov = 11))

month_sales <- month_sales[order(month_sales$month, decreasing = FALSE),]
month_sales$month <- month.abb[month_sales$month]
month_sales$month <- factor(month_sales$month, levels = month_sales$month)

month_sales |> 
  ggplot(mapping = aes(x = month, y = n)) +
  geom_col() + 
  theme_classic() +
  labs(x = "Month",
       y = "Number of Sales")
```

@@

coeff <- c(0, 0.36, 0.83, 1.03, 1.72, 0.31, 1.13, 0.58)
months <- c("April", "May", "June", "July", "August", "September", "October", "November")
month_results <- data.frame(Months = months, Coefficients = coeff)
month_results$Months <- factor(month_results$Months, levels = month_results$Months)
